### 2012-08-14 paper_sean/results.tex
Updated figure commands, added as many figures as possible.

\begin{figure}
\begin{center}
\vspace{1cm}
\epsfig{file=fit_gen.eps, width=8cm}
\caption[ ]{Fitnesses of the champion gaits averaged over 20 runs, measured in distance travelled over 12 seconds [cm/s]. These gaits outperformed gaits evolved in simulation using Genetic Algorithm by 54.3\% in simulation and 5.4\% better in reality while outperforming gaits evolved using HyperNEAT in hardware by 49.5\%.}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\vspace{1cm}
\epsfig{file=freq_fitness.eps, width=8cm}
\caption[ ]{Average frequencies of the gaits averaged over 20 runs. After implementing a policy which punished gaits with high frequencies, HyperNEAT was able to find high-performing, low frequency gaits. This policy was implemented to reduce servo shutdowns which heavily affected the reality performance of the robot.}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\vspace{1cm}
\epsfig{file=servo_pos.eps, width=8cm}
\caption[ ]{Top: A plot of servo positions for a gait produced in this study. Bottom: A plot of servo positions for a gait produced by HyperNEAT in hardware. Figure taken from Yosinski et al. \cite{yos:clune}. The smoothness, symmetry, and regularities of the top plot shows that by using a simulator, HyperNEAT was able to fully exploit the geometry of the problem.}
\end{center}
\end{figure}

>>>>

% \begin{figure}
% \begin{center}
% \vspace{1cm}
% \epsfig{file=fit_gen.eps, width=8cm}
% \caption[ ]{Fitnesses of the champion gaits averaged over 20 runs, measured in distance travelled over 12 seconds [cm/s]. These gaits outperformed gaits evolved in simulation using Genetic Algorithm by 54.3\% in simulation and 5.4\% better in reality while outperforming gaits evolved using HyperNEAT in hardware by 49.5\%.}
% \end{center}
% \end{figure}
\figp{aracna_notYetCleanedMultiPieceRobot_edit}{.6}{Fitnesses of the champion gaits averaged over 20 runs, measured in distance travelled over 12 seconds [cm/s]. These gaits outperformed gaits evolved in simulation using Genetic Algorithm by 54.3\% in simulation and 5.4\% better in reality while outperforming gaits evolved using HyperNEAT in hardware by 49.5\%. \edit{wrong fig, regenerate as pdf and add.}}

% \begin{figure}
% \begin{center}
% \vspace{1cm}
% \epsfig{file=freq_fitness.eps, width=8cm}
% \caption[ ]{Average frequencies of the gaits averaged over 20 runs. After implementing a policy which punished gaits with high frequencies, HyperNEAT was able to find high-performing, low frequency gaits. This policy was implemented to reduce servo shutdowns which heavily affected the reality performance of the robot.}
% \end{center}
% \end{figure}
\figp{aracna_notYetCleanedMultiPieceRobot_edit}{.6}{Average frequencies of the gaits averaged over 20 runs. After implementing a policy which punished gaits with high frequencies, HyperNEAT was able to find high-performing, low frequency gaits. This policy was implemented to reduce servo shutdowns which heavily affected the reality performance of the robot. \edit{wrong fig, regenerate as pdf and add.}}

% \begin{figure}
% \begin{center}
% \vspace{1cm}
% \epsfig{file=servo_pos.eps, width=8cm}
% \caption[ ]{Top: A plot of servo positions for a gait produced in this study. Bottom: A plot of servo positions for a gait produced by HyperNEAT in hardware. Figure taken from Yosinski et al. \cite{yos:clune}. The smoothness, symmetry, and regularities of the top plot shows that by using a simulator, HyperNEAT was able to fully exploit the geometry of the problem.}
% \end{center}
% \end{figure}
\figgp{aracna_notYetCleanedMultiPieceRobot_edit}{.6}{neat_110115_211410_00000_002_filt_zoom}{.6}{Top: A plot of servo positions for a gait produced in this study. Bottom: A plot of servo positions for a gait produced by HyperNEAT in hardware. Figure taken from Yosinski et al. \cite{yos:clune}. The smoothness, symmetry, and regularities of the top plot shows that by using a simulator, HyperNEAT was able to fully exploit the geometry of the problem. \edit{wrong fig on top, regenerate top fig as pdf and add.}}

### 2012-08-14 paper_sean/robot.tex
Updated figure commands, added as many figures as possible.

% figures
% figure of the quadratot in its natural stance
\begin{figure}
\begin{center}
\vspace{1cm}
% just using a photo from Haocheng's paper! Should replace if needed be           
\epsfig{file=quadratot_fig.eps, width=8cm}
\caption[ ]{The QuadraTot robotic platform. It is open-sourced and 3-D printable, which has allowed for other researchers to use the robot for their research around the world. The robot has 9 DOF, 2 per leg and a hip joint which connects the two symmetrical halves of the robot. The robot uses Dynamixel AX-18 and AX-12 servos for actuation. Figure taken from Shen et al. \cite{haocheng}.}
\label{fig:quadratot}
\end{center}
\end{figure}
%

\begin{figure}
\begin{center}
\vspace{1cm}
\epsfig{file=legpos.eps, width=8cm}
\caption[ ]{The figure shows an example of leg positions allowed and not allowed on the robot. The twoleft positions are allowed. The middle two positions are on the borderline. The right two positions are considered as ``fierce'' and are disallowed. Instead, these gaits are cropped to the middle two positions during gait performance by the cropping mechanism placed to prevent servo shutdowns. Figure taken from Shen et al. \cite{haocheng}}
\end{center}
\end{figure}
%

\begin{figure}
\begin{center}
\vspace{1cm}
\epsfig{file=gaitspace.eps, width=8cm}
\caption[ ]{A map of possible leg positions. Manually placed position cropping systems limited possible leg positions to avoid servo shutdowns and the robot hitting itself. The sum of the inner and outer servo positions cannot drop below 730, the smart cropping border, marked by the red line. Figure taken from Shen et al. \cite{haocheng}.}
\end{center}
\end{figure}
%

\begin{figure}
\begin{center}
\vspace{1cm}
\epsfig{file=wiimote.eps, width=8cm}
\caption[ ]{The Wiimote used to track the motion of ther robot. The Wiimote was used to track the IR LED placed on top of the robot and send the location data to a nearby computer which recorded the position of ther robot with respect to time. Figure taken from Yosinski et al. \cite{yos:clune}.}
\end{center}
\end{figure}

>>>>

% % figures
% % figure of the quadratot in its natural stance
% \begin{figure}
% \begin{center}
% \vspace{1cm}
% % just using a photo from Haocheng's paper! Should replace if needed be           
% \epsfig{file=quadratot_fig.eps, width=8cm}
% \caption[ ]{The QuadraTot robotic platform. It is open-sourced and 3-D printable, which has allowed for other researchers to use the robot for their research around the world. The robot has 9 DOF, 2 per leg and a hip joint which connects the two symmetrical halves of the robot. The robot uses Dynamixel AX-18 and AX-12 servos for actuation. Figure taken from Shen et al. \cite{haocheng}.}
% \label{fig:quadratot}
% \end{center}
% \end{figure}
% %
\figp{robot_whitebg}{.6}{The QuadraTot robotic platform. It is open-sourced and 3-D printable, which has allowed for other  researchers to use the robot for their research around the  world. The robot has 9 DOF, 2 per leg and a hip joint which connects  the two symmetrical halves of the robot. The robot uses Dynamixel  AX-18 and AX-12 servos for actuation. Figure taken from Shen et  al. \cite{haocheng}.}

% \begin{figure}
% \begin{center}
% \vspace{1cm}
% \epsfig{file=legpos.eps, width=8cm}
% \caption[ ]{The figure shows an example of leg positions allowed and not allowed on the robot. The twoleft positions are allowed. The middle two positions are on the borderline. The right two positions are considered as ``fierce'' and are disallowed. Instead, these gaits are cropped to the middle two positions during gait performance by the cropping mechanism placed to prevent servo shutdowns. Figure taken from Shen et al. \cite{haocheng}}
% \end{center}
% \end{figure}
\figp{sixLegPositions}{.6}{The figure shows an example of leg positions allowed and not allowed on the robot. The twoleft positions are allowed. The middle two positions are on the borderline. The right two positions are considered as ``fierce'' and are disallowed. Instead, these gaits are cropped to the middle two positions during gait performance by the cropping mechanism placed to prevent servo shutdowns. Figure taken from Shen et al. \cite{haocheng}}

% \begin{figure}
% \begin{center}
% \vspace{1cm}
% \epsfig{file=gaitspace.eps, width=8cm}
% \caption[ ]{A map of possible leg positions. Manually placed position cropping systems limited possible leg positions to avoid servo shutdowns and the robot hitting itself. The sum of the inner and outer servo positions cannot drop below 730, the smart cropping border, marked by the red line. Figure taken from Shen et al. \cite{haocheng}.}
% \end{center}
% \end{figure}
\figp{smartCrop}{.6}{A map of possible leg positions. Manually placed position cropping systems limited possible leg positions to avoid servo shutdowns and the robot hitting itself. The sum of the inner and outer servo positions cannot drop below 730, the smart cropping border, marked by the red line. Figure taken from Shen et al. \cite{haocheng}.}

% \begin{figure}
% \begin{center}
% \vspace{1cm}
% \epsfig{file=wiimote.eps, width=8cm}
% \caption[ ]{The Wiimote used to track the motion of ther robot. The Wiimote was used to track the IR LED placed on top of the robot and send the location data to a nearby computer which recorded the position of ther robot with respect to time. Figure taken from Yosinski et al. \cite{yos:clune}.}
% \end{center}
% \end{figure}
\figgp{wiiMote_crop.jpg}{.6}{robot_led_crop.jpg}{.6}{The Wiimote used to track the motion of ther robot. The Wiimote was used to track the IR LED placed on top of the robot and send the location data to a nearby computer which recorded the position of ther robot with respect to time. Figure taken from Yosinski et al. \cite{yos:clune}.}
